---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(dplyr)
library(knitr)
library(stringr)

all_fivethirtyeightdata_datasets <- data(package = "fivethirtyeightdata")$result[, c("Item", "Title")] %>%
  as_tibble()
```



# fivethirtyeightdata

`fivethirtyeightdata` is an add-on R data package to the [`fivethirtyeight`](fivethirtyeight-r.netlify.com/) package that contains user-contributed `vignettes/`
and `r all_fivethirtyeightdata_datasets %>% nrow()` datasets that could not be included in `fivethirtyeight` due to CRAN package size restrictions:

```{r echo=FALSE}
all_fivethirtyeightdata_datasets %>% 
  mutate(Item = str_c("`", Item, "`")) %>% 
  kable()
```

The released version of this package is accessed using a [drat](https://github.com/fivethirtyeightdata/drat) repository made using the `drat` package.


## Installation

You can run the following to get the latest released version of `fivethirtyeightdata`:

```r
install.packages(fivethirtyeightdata,
  repos = "https://fivethirtyeightdata.github.io/drat/",
  type = "source"
)
```

You can install the developmental version from [GitHub](https://github.com/fivethirtyeightdata/fivethirtyeightdata) with:

``` r
# install.packages("devtools")
devtools::install_github("fivethirtyeightdata/fivethirtyeightdata")
```

## Usage 

To load the `senators` dataset for example run:

```{r, eval = FALSE}
library(fivethirtyeight)
library(fivethirtyeightdata)
senators
```
