---
title: "fivethirtyeightdata"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{fivethirtyeightdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(fivethirtyeightdata)
```


`fivethirtyeightdata` is an add-on R data package that contains the large datasets not found in the original `fivethirtyeight` package hosted via a [drat](https://github.com/fivethirtyeightdata/drat) repository. The datasets are published by FiveThirtyEight \url{https://github.com/fivethirtyeight/data}.


## Datasets

The following datasets are available in full in this package:
```{r echo=FALSE}
library(magrittr)
data(package = "fivethirtyeightdata")$result[, c("Item", "Title")] %>%
  tibble::as_tibble()
```

## More Information

For more information, please visit the `fivethirtyeight` [GitHub](https://github.com/rudeboybert/fivethirtyeight) page and [website](fivethirtyeight-r.netlify.com/).